\section{Introduction}
\label{sec:intro}

%\textcolor{red}{The motivating Problem, why it's interesting or important}

Rating prediction plays an important role in the recommendation system as to capture users' preference for specific product. In Yelp, user can post their rating and review for a restaurant they visited, and these data as well as user/restaurant related attributes, e.g., user average rating, restaurant location or category, can be well gathered for conducting the rating prediction. If a user's rating for a restaurant can be accurately predicted, Yelp would be able to recommend high rating product to the user which meets their preferences. 

The challenge in this problem lies in the feature selection and modeling processing. With multiple features related to a user's rating, picking up the effective features is quite important, which would significantly influence the prediction performance. Additionally, the modeling process which selects the best machine learning model for rating prediction is also critical, and it's necessary to gain insights about how the model functions, i.e., the inner mechanism of model. Previously, most machine learning processes have been conducted in a "black box", by just showing input and output. In our project, we aim at visualizing the whole process, including feature selection, best split, and model tree. The Decision Tree model is selected because its straightforward idea in classification, which would be beneficial for visualization. 
