\section{Related Work}
\label{sec:related} 

%\textcolor{red}{Summarize research related to your projects, minimum 8 citations. }

In this project, we deploy the visualization principles and techniques to make mechanism of the whole recommendation system(RS) transparent based on Yelp's public dataset\cite{}. A lot of research has been done on recommendation system and the RS techniques are broadly divided into two types: memory-based approach, which recommend business based on similarity or correlation between users\cite{}, and model-based approach, which use machine learning methods to predict user ratings\cite{}. In our project, we use decision tree from model-based approach\cite{} as our visualization example. 

Our visualization of modeling process mainly focus on four parts: feature engineering, best split analysis, feature ranking and model training. For feature engineering, we extract 22 features in total, includes user-related features(7), business-related features(3), user-category features(5) and review-related features(7). Among review-related features, we extract several advanced natural language processing(NLP) features like polarity\cite{} and subjectivity\cite{}. For best spllit analysis, we create a moveable threshold to study how this feature -- business average star, could influence the decision making(whether to recommend or not). When moving the threshold, the calculated accuracy and true positive rate\cite{} will be changed correspondingly and we can choose the threshold with highest accuracy as our decision tree's best split. In the part of feature ranking, we measure the importance of all 22 features based on the score retrieved by Xgboost\cite{}. Xgboost's feature importance method calculateds F score, which indicates how many times the feature split on. Higher the F score is, more important the feature is. In our feature ranking visualization, we use a radar graph to show the importance of all these features based on F score. The last step is model training, we use 100 users as an example. 80 users are used to train and 20 users are used to test. The top three features with highest F score are selected and used by the model. We visualize each users path and the overall test accuracy.